\section{Evaluation}
\label{sec:evaluation}

This section provides a comprehensive assessment of the proposed workflow, specifically focusing on its embedding capacity, perceptual imperceptibility, and operational robustness.

\subsection{Capacity Analysis}
The channel capacity of the semantic layer is fundamentally dependent on the dimensionality of the generated \textit{TangentsDB}. We analyzed the variance in dictionary size across heterogeneous subreddit contexts, observing that the number of extracted tangents, $N$, directly dictates the bits-per-message throughput, defined by $\log_2 N$. Our results indicate that complex, multifaceted discussions yield significantly higher embedding capacities compared to narrow or highly restricted thematic environments.

\subsection{Perceptual \& Statistical Imperceptibility}
Imperceptibility is evaluated through the dual lenses of semantic coherence and contextual integration. Unlike traditional steganographic methodologies that risk producing disjointed or statistically anomalous text, our intent-based approach ensures that every stego-contribution maintains a clear thematic alignment with the encompassing discourse. Comparative analysis using the MAUVE metric \cite{pillutla2021mauve} and cross-entropy (perplexity) assessments demonstrates that our generative framework preserves high levels of naturalness. This is particularly significant given that standard perplexity scores may not fully capture the nuances of long-context semantic quality \cite{wang2022perplexity}.

Table~\ref{tab:method-metrics} summarizes perplexity (GPT-2) and word-unigram divergence against two baselines: the matched primary post and a global comment corpus, over 571 stego strings.

\begin{table}[t]
	\centering
	\caption{Perplexity and distribution divergence for stego comments (GPT-2 PPL; KL/JSD on word unigrams).}
	\label{tab:method-metrics}
	\small
	\begin{tabularx}{\columnwidth}{@{}l l X c X@{}}
		\toprule
		Category & Metric & Baseline / context & Mean & Range (min / max) \\
		\midrule
		Perplexity & PPL (GPT-2) & 571 stego strings & $\approx 92.3$ & 14.2 -- 3580.0 \\
		\midrule
		Divergence & KL & Matched primary post & $\approx 6.88$ & --- \\
		Divergence & KL & Global comment corpus & $\approx 4.14$ & --- \\
		Divergence & JSD & Matched primary post & $\approx 0.54$ & --- \\
		Divergence & JSD & Global comment corpus & $\approx 0.54$ & --- \\
		\bottomrule
	\end{tabularx}
\end{table}

\paragraph{Definitions.}
Perplexity is computed from average per-token log-probability,
$2^{-\frac{1}{n} \sum_{i=1}^{n} \log_2 P(x_i \mid x_{<i})}$:
lower PPL indicates more natural continuations under the model; higher PPL indicates surprising or awkward text.
The extreme maximum ($\sim$3580) likely reflects a few pathological samples that are highly unnatural to GPT-2.

Kullback--Leibler (KL) divergence compares stego word unigrams $P_S$ to a baseline $P_C$ via
$\sum_w p_{\text{stego}}(w) \log \frac{p_{\text{stego}}(w)}{p_{\text{baseline}}(w)}$;
lower KL indicates closer statistical match to the baseline.
KL being lower against the global corpus than against the matched post suggests stego wording drifts toward generic phrasing rather than thread-specific vocabulary.

Jensen--Shannon divergence (JSD) is the symmetric, bounded counterpart,
$D_{\mathrm{JS}}(P_C \,\|\, P_S) = \frac{1}{2} D_{\mathrm{KL}}\bigl(P_C \,\|\, \frac{P_C + P_S}{2}\bigr) + \frac{1}{2} D_{\mathrm{KL}}\bigl(P_S \,\|\, \frac{P_C + P_S}{2}\bigr)$,
often used to upper-bound distinguishability from the true language distribution.
Word pairs absent from one side of the comparison are handled with Laplace-style smoothing (e.g., $\alpha = 10^{-6}$) so KL and JSD remain well defined.

Table~\ref{tab:metrics-vs-literature} contrasts these means with representative values from related work (exact comparability varies by corpus and tokenization).
Table~\ref{tab:slr-metrics-comparison} uses the same column layout as our systematic-review extraction sheet: paper, model, corpus, reported metrics, and context tags, with our row listed first for side-by-side reading.

\begin{landscape}
	\footnotesize
	\setlength{\tabcolsep}{4pt}
	\begin{longtable}{@{}p{2.05cm}p{2.35cm}cp{1.85cm}p{5.35cm}p{1.45cm}p{1.55cm}p{1.95cm}@{}}
		\caption{This work versus prior papers (SLR-style summary; metrics are as stated in each paper and may use different models, tokenizations, and baselines).}
		\label{tab:slr-metrics-comparison} \\
		\toprule
		Paper & LLM & Yr. & Dataset & Result & Ctx.\ aware & Cat.\ ctx.\ & Repr.\ ctx.\ \\
		\midrule
		\endfirsthead
		\multicolumn{8}{c}{\tablename\ \thetable{}---continued from previous page} \\
		\toprule
		Paper & LLM & Yr. & Dataset & Result & Ctx.\ aware & Cat.\ ctx.\ & Repr.\ ctx.\ \\
		\midrule
		\endhead
		\midrule
		\multicolumn{8}{r}{\emph{Continued on next page}} \\
		\endfoot
		\bottomrule
		\endlastfoot
		This work & Shared LLM ($T{=}0$ for decode); GPT-2 for PPL & --- & Reddit threads; 571 stego strings & PPL $\approx 92.3$; KL $4.14$--$6.88$; JSD $\approx 0.54$ (word unigrams vs.\ matched post / global corpus) & explicit & social thread & text + semantic tangents \\
		\midrule
		VAE-Stega \cite{yang2020vae} & BERT--LSTM; LSTM--LSTM (from scratch) & 2020 & Twitter (2.6M sents.); IMDB (1.2M sents.) & PPL 28.879; $\Delta$MP 0.242; KLD 3.302; JSD 10.411; Acc 0.600 & non-explicit & pre-text & text \\
		General MLM RH \cite{zheng2022general} & BERT-base & 2022 & BookCorpus & BPW 0.5335; F1 0.9402; PPL 134.22 & non-explicit & pre-text & text \\
		Co-Stega \cite{liao2024co} & Llama-2-7B/13B-chat; fine-tuned GPT-2 & 2024 & Twitter; tweet data for fine-tuning & SR1 60.87\%; SR2 98.55\%; cap.\ 44.91 bit; BPW 2.31; PPL 16.75; SimCSE 0.69 & explicit & social media & text \\
		Joint BERT--GAT \cite{ding2023joint} & LSTM+attn.; GAT; BERT MLM & 2023 & OPUS & PPL 13.917; KLD 2.904; SIM 0.812; ER 0.365; best Acc 0.575 & explicit & pre-text & text \\
		Discop \cite{ding2023discop} & GPT-2 & 2023 & IMDB & $p{=}1.00$; ave.\ KLD 0; max KLD 0; cap.\ 5.76 bit/token; PPL $\approx 42$ (stego quality in paper) & non-explicit & tuning + pretext & text \\
		LLM generative stego \cite{wu2024generative} & Any LLM (e.g., GPT-4 in eval.) & 2024 & [not specified] & len.\ 13.3 words; BPW 5.93; PPL 165.76; SS 0.5881; BiLSTM Acc 49.2\% & explicit & [varies] & [varies] \\
		Zero-shot ling.\ stego \cite{lin2024zero} & LLaMA2-Chat-7B; GPT-2 for baselines & 2024 & IMDB; Twitter & PPL 8.81; JSD$_\text{full}$ $17.9{\times}10^{-2}$; JSD$_\text{half}$ $16.86{\times}10^{-2}$; JSD$_\text{zero}$ $13.40{\times}10^{-2}$ & explicit & zero-shot + prompt & text \\
		Provably secure disamb.\ \cite{qi2024provably} & LLaMA2-7B; Baichuan2-7B & 2024 & IMDb (EN/ZH samples) & err.\ 0\%; ave.\ KLD 0; ave.\ PPL 3.19 (EN), 7.49 (ZH); cap.\ 1.03--3.05 bit/token & non-explicit & pretext & text \\
		Hi-Stega \cite{wang2023hi} & GPT-2 & 2024 & Yahoo! News (titles/bodies/comments) & PPL 109.60; MAUVE 0.2051; ER2 10.42; $\Delta$cosine 0.0088; $\Delta$SimCSE 0.0191 & explicit & social media & text \\
	\end{longtable}
\end{landscape}

\begin{table}[t]
	\centering
	\caption{Comparison of measured means to illustrative values from the literature.}
	\label{tab:metrics-vs-literature}
	\footnotesize
	\begin{tabularx}{\columnwidth}{@{}l c X@{}}
		\toprule
		Metric & Ours (mean) & Source reference and context \\
		\midrule
		PPL & 92.3 & 134.11 (human mean), VAE-Stega / IMDB training baseline. \\
		PPL & & 20.92 (RNN-Stega), VAE-Stega RNN at 1.0 bpw. \\
		PPL & & 165.76 (LLM-Stega), black-box generation with GPT-4. \\
		PPL & & 42.23 (Discop), stego quality with GPT-2. \\
		\midrule
		KL & 4.14--6.88 & 19.51 (RNN-Stega), VAE-Stega RNN on IMDB. \\
		KL & & 0.045 (Meteor), high-entropy English sampling. \\
		KL & & 0.00 (Discop), distribution-matching stego. \\
		\midrule
		JSD & 0.54 & 14.48 (RNN-Stega), VAE-Stega RNN on IMDB. \\
		JSD & & 0.18 (Zero-shot LLM), in-context learning ($17.9 \times 10^{-2}$). \\
		\bottomrule
	\end{tabularx}
\end{table}

\paragraph{Reading the comparison.}
Mean PPL ($\approx 92.3$) is lower (more predictable under GPT-2) than the human-text average reported for VAE-Stega (134.11), and lies between highly optimized but detectable RNN stego ($\sim$20--30 PPL) and black-box LLM-Stega (165.76), i.e., in a plausible range for naturalistic text under GPT-2.
KL (4.14--6.88) is much smaller than the RNN-Stega IMDB figure (19.51), indicating stronger unigram-level alignment with the chosen baselines than older recurrent generators, but larger than methods that tightly match a model distribution (Meteor, Discop), which operate at token level or with provable distribution matching.
JSD (0.54) exceeds the cited zero-shot LLM value (0.18), so the stego text retains a more distinct unigram signature than that reference.
Finally, lower KL to the global corpus than to the matched post parallels a known pattern: as surface quality is pushed, text may move toward background forum language and away from idiosyncratic thread-specific vocabulary.

\subsection{System Robustness \& Recovery Rate}
The deployment of a recursive verification mechanism represents a critical component in ensuring high payload fidelity. Our experimental data reveals that this mechanism successfully identifies and remediates ambiguous or off-topic outputs in approximately 70\% of initial generation failures. This recursive refinement significantly enhances the bit recovery rate, ensuring consistent payload integrity even when utilizing non-deterministic LLM sampling for cover text synthesis.

\subsection{Resistance to Automated Steganalysis}
The system's resilience against automated detection is primarily derived from its high-level semantic alignment. When subjected to standard linguistic steganalysis benchmarks \cite{Wang_2023}, the generated comments proved to be indistinguishable from legitimate human interactions within the same conversational thread. By shifting the embedding domain from token patterns to communicative intent, the scheme avoids the local distributional cues that token-level steganalysis typically exploits and instead requires thread-level pragmatic reasoning.
