\section{Implementation}
\label{sec:implementation}

The practical implementation follows the same stage order as the workflow runner: data load, research, angle generation, stego synthesis, and decode. Each stage persists artifacts to disk so later stages can reuse the exact same corpus and hashes, which keeps the sender and receiver aligned across retries.

\subsection{Architectural Components}
The system is operationalized through a series of deterministic pipeline stages. Core components include:
\begin{itemize}
    \item \texttt{DataLoadPipeline}: Fetches unresolved URL content, replaces the post body with the extracted text, and caches normalized URL responses by SHA-256.
    \item \texttt{ResearchPipeline}: Generates search terms from the post title, text, and URL with an LM Studio model at \texttt{temperature=0}, caches them in a SQLite \texttt{research\_terms\_cache.db}, queries Google Custom Search, removes duplicate links and PDFs, and fetches page text in batches of three. The stage persists a flat \texttt{search\_results} corpus together with reproducibility hashes.
    \item \texttt{GenAnglesPipeline}: Flattens the corpus assembled from \texttt{selftext}, \texttt{search\_results}, and comments, then calls the angle runner to produce \texttt{source\_quote}/\texttt{tangent}/\texttt{category} triplets. Long inputs are split into 30k-character segments and batched up to 150k characters, and each prompt batch is logged and cached by input hash. If the backend path fails, the pipeline falls back to a direct LM Studio prompt that uses the same JSON schema.
    \item \texttt{StegoPipeline} and \texttt{DecodePipeline}: Combine the compression layer, comment targeting, semantic shortlist, and verification loop. The encoder generates three candidate comments per angle, decodes them immediately, and retries up to five attempts if the selected angle is not recoverable.
\end{itemize}

\subsection{Model Configuration}
The pipeline uses different models for different stages:
\begin{itemize}
    \item \textbf{URL extraction and search terms:} The crawl4ai extraction stage and the search-term generator default to \texttt{mistral-nemo-instruct-2407-abliterated} at \texttt{temperature=0}.
    \item \textbf{Angle generation:} The dedicated angle runner uses \texttt{openai/gpt-oss-20b} at \texttt{temperature=0}, validates raw JSON arrays, and repairs malformed responses when needed.
    \item \textbf{Stego synthesis:} The encoder uses \texttt{openai/gpt-oss-20b} at \texttt{temperature=0.7} to produce candidate Reddit-style comments.
    \item \textbf{Semantic matching and decode:} \texttt{all-MiniLM-L6-v2} performs cosine-similarity shortlist ranking, and \texttt{gpt-oss-20b} selects the final angle index at \texttt{temperature=0}.
\end{itemize}
