\section{Introduction}
\label{sec:introduction}

Linguistic steganography focuses on the covert embedding of secret information within ostensibly innocuous textual carriers. Traditional methodologies, primarily predicated on lexical substitution and synonym manipulation, often struggle with the inherent low redundancy of natural language. Consequently, even minor statistical deviations can provide sufficient signal for modern automated detection systems \cite{yang2020vae,kaptchuk2021meteor,Wang_2023}. The emergence of Large Language Models (LLMs) has catalyzed a paradigm shift, transitioning the field from text modification to de novo text generation \cite{liao2024co}. By sampling directly from a model's learned probability distribution, these generative approaches theoretically achieve high levels of statistical imperceptibility.

However, existing LLM-based steganographic systems remain constrained by the "Psic effect"—a fundamental trade-off between statistical security and perceptual naturalness \cite{yang2020vae}. While a model may output grammatically and statistically fluent sentences, these often lack the deep semantic coherence required for specific communicative contexts, such as threaded social media discussions. A comment that is technically flawless yet pragmatically irrelevant to the ongoing discourse serves as a conspicuous anomaly under human or semantic-level scrutiny.

To address these challenges, we introduce a context-aware steganographic framework that elevates the embedding domain from the lexical level (individual tokens) to the semantic level (communicative intents). Instead of manipulating distribution probabilities, our approach analyzes the target conversational context to synthesize a dynamic repository of "Tangents"—relevant, thematic conversation angles. Secret payloads are encoded through the selection of specific Tangents, which are subsequently expanded by an LLM into natural, contextually appropriate responses. This ensures that the generated stego-text is not only statistically robust but also pragmatically integrated into the target environment. A specialized verification agent closes the loop, guaranteeing that the intended semantic orientation remains recoverable prior to transmission.

The primary contributions of this paper are:
\begin{itemize}
    \item A novel "Semantic Steganography" architecture that encodes data into high-level communicative intents, significantly enhancing resistance to semantic analysis.
    \item A dynamic, context-driven dictionary generation mechanism that achieves operational parity between sender and receiver through deterministic search and retrieval.
    \item A closed-loop verification system utilizing an agentic Supervisor to ensure message recoverability and cross-contextual alignment.
\end{itemize}
