\section{Methodology}
\label{sec:methodology}

This research proposes a black-box steganographic technique that embeds information within the semantic architecture of a conversation. The methodology is predicated on a standard covert communication scenario involving Alice (the sender) and Bob (the receiver), communicating over a public social media platform. While this study utilizes Reddit as a primary case study, the underlying principles are platform-agnostic and transferable to any threaded discussion environment.

\subsection{System Architecture}
The core of the proposed framework centers on a multi-layer embedding process that leverages both the \textit{spatial location} of the response and the \textit{thematic subject} of the content as carriers for the secret payload. By mapping binary data to high-level conversational actions—specifically, the selection of a reply target and the determination of a tangent—the system maximizes channel capacity while preserving perceptual naturalness. In a passive discovery scenario, the receiver monitors the sender's public profile to identify recent interactions, which serve as the requisite entry points for the de-steganography process.

\subsection{Operational Requirements}
To achieve synchronization, both the sender and receiver must maintain access to:
\begin{itemize}
    \item \textbf{Public Communication Channel:} Accounts on the target social media platform.
    \item \textbf{Shared Operational Parameters:} A deterministic search algorithm, target identifiers (URLs or hashtags), and predefined search constraints.
    \item \textbf{Synchronized LLM Configuration:} Access to an identical Large Language Model (or API) with a fixed \texttt{temperature=0} setting, ensuring deterministic output during the codebook construction phase.
\end{itemize}

\subsection{Deterministic Search \& Synchronization Modes}
Ensuring that both parties construct an identical \textit{TangentsDB} from dynamic online content is critical for reliable decoding. We adopt operational modes inspired by the OPPRESSION framework \cite{zillien2024oppression} to maintain consistency:

\begin{enumerate}
    \item \textbf{Ephemeral Mode (Temporal Snapshots):} For highly dynamic environments, both parties capture a "snapshot" of a document set at a synchronized temporal reference. Alice utilizes a precise timestamp $t_{snap}$ alongside fixed search criteria (e.g., "return the 1,000 most recent posts for hashtag X"). Upon observing the stego-contribution, Bob retrieves the same stream using the identical timestamp and parameters, thereby ensuring parity despite platform-level fluctuations.
    \item \textbf{Persistent Mode (Immutable Versioning):} For scenarios requiring long-term consistency, the system leverages resources with immutable version histories. This involves referencing specific historical versions of encyclopedic entries (e.g., Wikipedia via \texttt{oldid}) or archived digital texts, guaranteeing bit-for-bit identity regardless of access time.
\end{enumerate}

To further guarantee state synchronization, Alice generates a \textbf{Cryptographic Hash} of the selected document set. This hash (or a truncated representation) can be embedded within the primary layer, allowing Bob to verify dataset integrity before proceeding with the decoding sequence. This mechanism effectively mitigates the "Shared Algorithm Gap," where search results might otherwise diverge due to algorithmic personalization or geofencing.

\subsection{State Synchronization (Temporal Window)}
To ensure that both Alice and Bob visualize an identical state of the conversation tree, they must adhere to a negotiated \textit{Temporal Window Duration} ($T_{sync}$). This synchronization mechanism is operationalized as follows:
\begin{enumerate}
    \item \textbf{Sender Side:} Alice captures a snapshot of the discussion thread at time $t_{start}$ and subsequently publishes the generated stego-comment at $t_{publish}$.
    \item \textbf{Receiver Side:} Upon identifying the stego-contribution published at $t_{publish}$, Bob filters the thread's historical state to include only those comments established prior to $t_{publish} - T_{sync}$.
\end{enumerate}
This protocol ensures that the "Comment Chain" retrieved by the receiver precisely replicates the context available to the sender during generation. In instances where the sender's generation and verification cycles exceed $T_{sync}$, state divergence may occur. To mitigate this, the sender may leverage an extended window or transmit a minimal adjustment signal via a secondary channel or within the primary payload.

\subsection{Payload Optimization \& Compression}
Prior to embedding, the raw payload undergoes a transformation layer designed to minimize bitstream length and maximize efficiency. We implement a \textit{dynamic dictionary-based compression} scheme:
\begin{enumerate}
    \item \textbf{Dictionary Synthesis:} A session-specific linguistic dictionary is synthesized from the encompassing conversational context (post text and existing comments) and the broader domain-specific documents retrieved via search.
    \item \textbf{Bitstream Transformation:} The secret payload is encoded using references to this dynamic dictionary (e.g., utilizing a tuple format: \textit{Document Index, Offset, Length}), falling back to an efficient literal encoding for unique sequences.
\end{enumerate}
This ensures that the payload is reduced to its minimal binary representation before being partitioned for multi-layered embedding.

\subsection{Two-Layer Semantic Embedding Architecture}

\subsubsection{Layer 1: Spatial Embedding (Reply Targeting)}
The primary embedding layer determines the \textit{architectural placement} of the steganographic contribution within the conversation tree.
\begin{enumerate}
    \item The system retrieves the comprehensive comment structure of the target post, subject to the $T_{sync}$ constraint.
    \item This tree is flattened into a deterministic sequence of available comments, ordered by an immutable attribute (e.g., \textit{Creation Timestamp} or \textit{Unique Identifier}).
    \item A specific segment of the compressed payload determines the index of the reply target.
    \item \textbf{Resultant State:} A designated \texttt{Target Comment Chain}.
\end{enumerate}

\subsubsection{Layer 2: Intent-Based Embedding (Thematic Tangent Selection)}
The secondary layer determines the \textit{communicative intent} of the generated text.
\begin{enumerate}
    \item \textbf{Contextual Expansion:} The system extracts salient search terms from both the original post and the selected comment chain, initiating a retrieval-augmented search to gather external domain knowledge.
    \item \textbf{Contextual Pool Construction:} A unified repository is assembled from: (1) the source post, (2) the relevant comment chain, and (3) the retrieved search results.
    \item \textbf{Thematic Perspective Mapping:} Each document within the pool is processed by the synchronized LLM using a structured prompt to distill "Tangents"—potential thematic directions for conversation.
    \item \textbf{Deterministic Serialization:} To ensure consistent bit-to-index mapping, the extracted Tangents are serialized into a single list. The ordering of this list is strictly derived from the deterministic sort order of the source documents, guaranteeing that both Alice and Bob generate identical codebook indices.
    \item \textbf{Thematic Selection:} The corresponding payload bits are mapped to a specific tangent within the serialized list.
    \item \textbf{Resultant State:} A specific \texttt{Target Tangent} comprising a Category, Tangent, and Source Context.
\end{enumerate}

\subsection{Generative Synthesis \& Verification}
Following the selection of the target context and thematic tangent, the sender initiates the cover text synthesis process.
\begin{itemize}
    \item \textbf{Synthesis:} A generative LLM (configured with \texttt{temperature > 0}) constructs a response that explores the \texttt{Target Tangent} while maintaining the appropriate \texttt{Thematic Category}. The model utilizes the \texttt{Target Comment Chain} as context to ensure pragmatic integration.
    \item \textbf{Verification Loop:} Before the stego-text is committed to the public channel, the sender executes a local \textit{Decoding Simulation}.
    \item \textbf{Recursive Refinement:} If the simulation fails to accurately recover the intended angle, the sender re-executes the synthesis step. The non-zero temperature ensures variations in output; this process iterates until a verifiable stego-text is achieved.
\end{itemize}

\subsection{Decoding \& Intent Recovery}
The receiver, identifying the \texttt{Target Comment Chain} post-hoc, reconstructs the identical Contextual Pool and serialized Tangents list. To recover the hidden intent (Layer 2):
\begin{enumerate}
    \item \textbf{Semantic Filtering:} The receiver employs a semantic similarity model to compare the observed stego-text against the pool of potential Tangents, identifying the top $N \approx 50$ candidates.
    \item \textbf{Discriminative Identification:} A specialized LLM prompt is executed on these candidates to achieve precise identification:
          \begin{quote}
              \textit{"Identify the specific tangent from the provided candidates... return the index only."}
          \end{quote}
\end{enumerate}
This high-precision recovery mechanism ensures the robust extraction of the hidden payload with minimal error rates.
